\textcolor{violet}{Reverse Correlation Uncovers More Complete Tinnitus Spectra \vspace{0.25cm}}

### 2023-03-29 paper/short/main_wc995.tex
Update paper

Ten ($n=10$) normal-hearing subjects listened to \textit{A-X} trials containing a target sound ($A$) followed by a stimulus ($X$).
$X$ was randomly generated for each trial, while $A$ remained the same within a block of $100$ trials (Fig.
\ref{fig:experimentdiagram}).
Subjects completed two (2) blocks per target sound ($p=200$ total trials per subject).
Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
Subjects listened over earphones at a self-determined comfortable level, which they adjusted themselves while listening to sample stimuli.
Presentation level was not recorded.
Procedures were approved by the UMass IRB.

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{gfx/experiment_overview.pdf}
  \caption{Diagram of the experimental protocol.
  Subjects listen to a series of random stimuli,
  each preceded by a target sound.
  Subjects compare the stimulus to the target, and respond either ``yes'' or ``no''
  depending on their perceived similarity.
  The recorded stimulus-response pairs are used to form an estimate of the target.}
  \label{fig:experimentdiagram}
\end{figure}

>>>>

Ten ($n=10$) normal-hearing subjects listened to \textit{A-X} trials containing a target sound ($A$) followed by a stimulus ($X$).
$X$ was randomly generated for each trial, while $A$ remained the same within a block of $100$ trials (Fig.
\ref{fig:experimentdiagram}).
Subjects completed two (2) blocks per target sound ($p=200$ total trials per subject).
Subjects were told that some stimuli had $A$ embedded in them, and were instructed to respond ``yes'' to such stimuli, otherwise ``no.''
Subjects listened over earphones at a self-determined comfortable level.
Presentation level was not recorded in this study.
Procedures were approved by the UMass IRB.

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{gfx/fig1.pdf}
  \caption{Diagram of the experimental protocol.
  Subjects listen to a series of random stimuli,
  each preceded by a target sound.
  Subjects compare the stimulus to the target, and respond either ``yes'' or ``no''
  depending on their perceived similarity.
  The recorded stimulus-response pairs are used to form an estimate of the target.}
  \label{fig:experimentdiagram}
\end{figure}
